Irt plot extra

### 2022-03-27 manuscript.Rmd
EFA combined plot updated

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line(colour ='#DC000099')+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=1.5,colour ='#3C5488FF')+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
  scale_x_continuous(name="Factor Number", limits=c(0, 20),breaks=seq(0,20,4))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
#text = element_text(size = 25

@@

# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
  apatheme +theme(legend.position = "None") +scale_fill_identity()

>>>>

scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
   geom_line(colour ='#DC000099')+
  #geom_line(data = PA.Scree)+ 
  geom_point(size=1.5,colour ='#3C5488FF')+
  #geom_point(data = PA.Scree, size=3)+
  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
  scale_x_continuous(name="Factor Number", limits=c(0, 18),breaks=c(0,6,18))+
  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None")
#text = element_text(size = 25

@@

# HULL
EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
  apatheme +theme(legend.position = "None") +scale_fill_identity()+
  scale_x_continuous(breaks=c(0,5,12))
